---
title: "Capstone project"
author: "Anurag Agrawal"
date: "12/05/2021"
output: word_document
---

######################################## What you will learn and Implement #######################################

# > Understand kmeans clustering.
# > Understand retail Data for applying kmeans clustering.
# > Understand the objective.
# > Maths of kmeans clustering.
# > understand Optimum number of cluster.
# > Using elbow method to determine the optimal number of cluster.
# > model fitting
# > Evaluation

# > Objective

# The client is a leading Fashion retailer in Australia. Company runs a display advertising campaign for this brand, where it shows ads to users leading them to make a purchase on the brands website.The given dataset is the Sales data for all users who made a purchase online in the first half of October '17.

# Based on your analysis, arrive at a statistical segmentation of the brands audience based 
# on Revenue. The number of segments is up to you. Please provide definitions of each groups

# > desired Library installation

```{r}
# install.packages("factoextra")
# install.packages("rpivotTable")
# install.packages("cluster")
# install.packages("fpc")
# install.packages("factoextra")
#install.packages("rpivotTable")
# install.packages("ggplot2")
# install.packages("dplyr")
# install.packages("magrittr")
```


```{r}

library(ggplot2)
library(dplyr)
library(magrittr)
library(cluster)
library(fpc)
library(factoextra)
library(purrr)
library(rpivotTable)
```

# > Setting working directory

```{r}
path = 'C:/Users/anura/Desktop/Capston Project 1'
setwd(path)
getwd()
```

# > reading data

```{r}
D<-read.csv("RevenueCluster.csv",header = TRUE)
D

str(D)
```

# #> subsetting/manipulating data to fit kmeans clustering

```{r}
#columns names
names(D)

#visulize data
data.table::data.table(D)#head
head(D[,-c(1,2,3,4)]) #1st way
head(D[, c(5)]) #2nd way
model_km <- kmeans(D[, c(5)], centers = 3)

print(model_km)

clust_km <- factor(if_else(model_km$cluster == 1, 1, 0))

head(clust_km, 50)
```

# > fitting basic model taking a random number of cluster say "3"

```{r}

k <- kmeans(D[, -c(1,2,3,4)],centers = 3)
k
```

# > calculating optimum number cluster

```{r}
optimcluster <- function(K){
  cluster <- kmeans(RevenueCluster[, c(5)], 3)
  return(cluster$tot.withinss)
}

wss <- sapply(1:20, optimcluster)

optimK <- data.frame(k = 1:20, wss)
head(optimK)
```

Interpretation: The method consists of plotting the explained variation as a function of the number of clusters, and picking the elbow of the curve as the number of clusters to use.

### ploting the k value from 1 to 20 against within sum of square (wss)

```{r}
ggplot(data = optimK) + aes(x=k, y= wss) + geom_point() + geom_line()+
  scale_x_continuous(breaks = seq(1,20,by = 1))

OptimunCluster <- "Enter a number which is optimum for Analysis"
```

# > Model fitting using optimum k

```{r}
library(dplyr)
cats <- select_if(D, is.character)
table(cats$Private)

nums <- select_if(D, is.numeric)
summary(nums)


str(D)

model_1 <-
  glm(
    Private ~ Revenue(AUD),
    family = binomial(link = 'logit'),
    data = D
  )

```


```{r}
write.csv()
```

